Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-03-02 draft.tex
remove lowercase state variables throughout sec. 2

If both $s$ and $g$ play Status Quo, then the status quo persists. The status quo payoffs for the secessionists are modeled as a state variable. The transition of this state variable from one period to the next involves an increase by the amount of the patron's investment and an automatic reduction by $\mu$.\footnote{Note that it is also possible for the international community to make an investment in the secessionists' status quo payoffs, but we will show that they have no incentive to do so.} The steady reduction by $\mu$ represents the costs of non-recognition discussed in the introduction. As the economy in the secessionist region deteriorates, so does the standard of living for the secessionists. Therefore, the payoffs from the status quo, in the absence of other actions, are given by $q_s^{t+1} = Q_s^t - \mu$. Lower case letters denote beginning-of-period quantities net of investments by outside actors, while upper case letters denote end-of-period quantities gross of such investments.

Other payoffs are also modeled as state variables. However, they remain unchanged from period to period unless players $p$ or $c$ make an investment, e.g. $L_s^t = l_s^t + R_p^t + R_c^t$ and $l_s^{t+1} = L_s^t$, likewise for player $g$ and for the payoffs from winning for both players and the status quo for player $g$.

@@

At the start of each period, the patron, $p$, and player $c$ may invest resources to affect the payoffs of $s$ and $g$ in the stage game. For example, if $p$ expends resources $R_p^t$ to increase the secessionists' status quo payoffs, the beginning-of-period payoff $q_s^t$ becomes end-of-period payoff $Q_s^t = q_s^t + R_p^t$. We can write analogous expressions for $q_g^t, \ l_s^t,\ l_g^t,\ w_s^t$, and $w_g^t$, and the international community can also make investments to increase whichever of these payoffs they like. $B_p^t$ denotes the total that the patron can devote to interceding in the conflict; we assume that player $c$, which is often a large coalition of states, does not have a binding budget constraint.

>>>>

If both $s$ and $g$ play Status Quo, then the status quo persists. The status quo payoffs for the secessionists are modeled as a state variable. The transition of this state variable from one period to the next involves an increase by the amount of the patron's investment and an automatic reduction by $\mu$.\footnote{Note that it is also possible for the international community to make an investment in the secessionists' status quo payoffs, but we will show that they have no incentive to do so.} The steady reduction by $\mu$ represents the costs of non-recognition discussed in the introduction. As the economy in the secessionist region deteriorates, so does the standard of living for the secessionists. Therefore, the payoffs from the status quo evolve according to the following law of motion: $Q_s^{t} = Q_s^{t-1} - \mu + R_p^t - R_c^t$.\footnote{Here we anticipate a bit the incentives of the patron and international community in the next section to sign the impact of contributions: the patron will want to increase the value of the status quo to the secessionists, while the international community could only desire to reduce this value.}

Other payoffs are also modeled as state variables. However, they remain unchanged from period to period unless players $p$ or $c$ make an investment, e.g. $L_s^t = L_s^{t-1} - R_p^t + R_c^t$ and similarly for player $g$ and for the payoffs from winning for both players and the status quo for player $g$.

@@

At the start of each period, the patron, $p$, and player $c$ may invest resources to affect the payoffs of $s$ and $g$ in the stage game. For example, if $p$ expends resources $R_p^t$ to increase the government's payoffs from ceding, the previous period's payoff $L_g^{t-1}$ is augmented so that $L_g^t = L_g^{t-1} + R_p^t$. We can write analogous expressions for any of the state variables, recalling that the international community can also make investments to increase whichever of these payoffs they like. $B_p^t$ denotes the total that the patron can devote to interceding in the conflict; we assume that player $c$, which is often a large coalition of states, does not have a binding budget constraint.
